---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nsapi
The Dutch National Railway service (NS; Nederlandse Spoorwegen) has an API where we can
query for travel advise, see the current trains on a given station, see if there is any delays or work on the tracks and NS also provides a list with geolocation of all the stations. 

The goal of nsapi is to make it easy to gather data from the NS api. The package strives to return data.frames

## Installation

You can NOT YET install the released version of nsapi from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("nsapi")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("RMHogervorst/nsapi")
```
## Example

This is a basic example which shows you how you get travelinformation:

```{r}
library(nsapi)
```

```{r example}
treinplanner <- travel_advise(
  fromStation = "Leiden Centraal", 
  toStation = "Utrecht Centraal",
  departure = TRUE,
  yearCard = TRUE,
  previousAdvices = 1, 
  nextAdvices = 1)
treinplanner
```





## Metadata
The package is MIT licensed although the information from NS is probably propriatary.

```{r, eval=FALSE}
codecoverage <- covr::package_coverage(path = ".",type = "tests")
print(codecoverage)
```

